---
title: "DATA VIS HW2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#for interactive visualizations
#library(rbokeh)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(plotly)
library(ggthemes)
#install.packages('maps')
library(maps)
#loading appropriate packages
library(sf)
library(tigris)
#options(tigris_use_cache = TRUE)
#options(tigris_class="sf")
library(tmap)
library(tibble)
library(stringr)


```

```{r}
#Loading and reading our storms dataset
storms<-read.csv("/Users/inesperezalvarez-pallete/Downloads/storms.csv")
#summary(storms)
```

```

## Q1:1. Damage from Storms

###a) State Level Choropleth Maps
Provide a static state-level choropleth map of the United States visualizing where monetary damage is recorded (by using the sum of the variables DAMAGE_PROPERTY_USD and DAMAGE_CROPS_USD).

```{r Q1A}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(plotly)
library(ggthemes)
#install.packages('maps')
library(maps)
#loading appropriate packages
library(sf)
library(tigris)
#options(tigris_use_cache = TRUE)
#options(tigris_class="sf")
library(tmap)
library(tibble)
library(stringr)
library(maps)
# Loading US state map data
us.states <- map_data("state")

# Plotting the US map
ggplot() + 
  geom_polygon(data = us.states, aes(x = long, y = lat, group = group), color = "grey", fill = NA) +
  coord_map(projection = "azequidistant")

# Preparing the map data to merge with the storms dataset
# Add State Abbreviations and Centers
#statenames <- as_tibble(
 # cbind(state=tolower(state.name), state.abb = state.abb, 
  #     state.center.x = state.center$x, 
   #     state.center.y = state.center$y))
        
  statenames <- tibble(
  state = c("texas", "louisiana", "florida", "georgia"), 
  state.abb = c("TX", "LA", "FL","GA"), 
  state.center.x = c(-98.8,-92.3,-81.7,-83.3736),
  state.center.y = c(31.4,30.6,27.9,32.3329)
)

statenames <- statenames %>% mutate_at(funs(as.numeric), 
                 vars=c("state.center.x","state.center.y"))

#us.states <- left_join(us.states, statenames, by = c('region','state'))
#str(us.states)

storms_cost <- storms %>%
  mutate(region = tolower(STATE)) %>%
  # Converting state names to lowercase
  mutate(tot_damage_per_event = DAMAGE_PROPERTY_USD + DAMAGE_CROPS_USD) %>%
  mutate(year=YEAR)
  
storms_cost <- storms_cost %>%
  group_by(region) %>%
  summarise(tot_damage = sum(tot_damage_per_event, na.rm = TRUE) / 100000)

# Merge with state data
state.merged <- left_join(storms_cost, us.states, by = 'region')
  
# Merge with year data
#state.merged <- left_join(state.merged, year_data, by = 'region') %>%
  # summarise(tot_damage = sum(tot_damage))

# Merge county map with total damage


#clean data to eliminate any states that present NA abbreviations
#state.merged <- dplyr::filter(state.merged, state.abb!="NA")

# Preprocessing storm data to compute the total sum of property and crop damage over the time period

cost_map <-ggplot(state.merged, aes(x = long, y = lat, group = group, fill = tot_damage)) +
  geom_polygon(color = "grey") +
  coord_map(projection = "mercator") +
  scale_fill_gradientn(colors = c("lightblue", "red"), name = "Total Damage (hundred-thousand USD)")  +geom_text(data=statenames, inherit.aes = FALSE, 
            aes(label=state.abb, x=state.center.x, 
                y=state.center.y), colour="white")+theme_map()+labs(title="Total Damages by Severe Weather 2017-2022")+ theme(legend.position="bottom", panel.border = element_blank())
 
print(cost_map)

  ##CREATING FACET WRAPPING TO SHOW 5 YEAR DIFFERENCE
  
  library(ggplot2)
library(dplyr)

# Calculate total damage per region per year

summary_data <- storms %>%
  mutate(region = tolower(STATE)) %>%  # Converting state names to lowercase
  mutate(tot_damage_per_event = DAMAGE_PROPERTY_USD + DAMAGE_CROPS_USD) %>%  # Calculate total damage per event
  group_by(region, year = YEAR) %>%  # Group by region and year
  summarise(total_damage = sum(tot_damage_per_event, na.rm = TRUE) / 1000000,.groups = 'drop')  %>% 
  group_by(region)
  
  # Summarize total damage

# Merge with state data
dyn_merged <- left_join(summary_data, us.states, by = 'region', relationship="many-to-many")

# Create base plot, with facets for each year
base_plot <- ggplot(dyn_merged, aes(x = long, y = lat, group = group, fill = total_damage)) +
  geom_polygon(color = "grey") +
  coord_map(projection = "mercator") +
  scale_fill_gradientn(colors = c("lightblue", "red"), name = "Total Damage (Million USD)") +
  theme_map() +
  labs(title = "Total Damages by Severe Weather 2017-2022") +
  theme(legend.position = "bottom", panel.border = element_blank()) +
  facet_wrap(~ year)  # Create facets for different years

# Print base plot
print(base_plot)
  
 ##Converting into dynamic map

 # ungroup()

#lets animate our plot

library(ggplot2)
library(gganimate)
library(dplyr)


```



  ### Q1B, Creating a county-level choropleth
Provide a static county-level choropleth map of the United States visualizing where monetary damage is recorded (by using the sum of the variables DAMAGE_PROPERTY_USD and DAMAGE_CROPS_USD).


```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(plotly)
library(ggthemes)
#install.packages('maps')
library(maps)
#loading appropriate packages
library(sf)
library(tigris)
#options(tigris_use_cache = TRUE)
#options(tigris_class="sf")
library(tmap)
library(tibble)
library(stringr)
library(maps)
# Loading US state map data
us.states <- map_data("state")
#devtools::install_github("UrbanInstitute/urbnmapr")
#uploading county map shapefile from US Census Bureau Data
#install.packages('rgdal')
library(ggthemes)
require(sf)
library(urbnmapr)
#us county map

us.counties <- map_data("county")
uscounties_sf<-get_urbn_map("counties",sf=TRUE)


# If it's an old-style CRS, update it to a newer format
#uscounties_sf <- st_set_crs(uscounties_sf, value = NA)

# Now, mutate the county_name column
uscounties_sf <- uscounties_sf %>%
  mutate(county_name = tolower(county_name))
# devtools::install_github("UrbanInstitute/urbnmapr")


#display our map shape files, by county
# Update the CRS of the uscounties_sf object
#uscounties_sf <- st_transform(uscounties_sf, #crs = st_crs(4326))

# Plot the spatial object
ggplot(uscounties_sf) + geom_sf() + theme_map()


#preprocessing data to calculate total damage, by county
county_cost <- storms %>%
  mutate(
    tot_damage_per_event = DAMAGE_PROPERTY_USD + DAMAGE_CROPS_USD,
    county_fip = ifelse(nchar(CZ_FIPS) == 1, paste0("00", CZ_FIPS),
                        ifelse(nchar(CZ_FIPS) == 2, paste0("0", CZ_FIPS), CZ_FIPS)),
    state_fip = ifelse(nchar(STATE_FIPS) == 1, paste0("0", STATE_FIPS), STATE_FIPS),
    county_fips = paste0(state_fip, county_fip),
    county_name = tolower(CZ_NAME)
  ) %>%
  group_by(county_fips) %>%
  summarise(total_damage = sum(tot_damage_per_event, na.rm = TRUE) / 100000) %>%
  filter(total_damage > 0)
  
#uscounties_sf <- get_urbn_map("counties", sf = TRUE)

# Ensure correct CRS format and convert county names to lowercase
#uscounties_sf <- st_set_crs(uscounties_sf, value = NA) %>%
 # mutate(county_name = tolower(county_name))

# Preprocessing data to calculate total damage by county

county_cost <- storms %>%
  mutate(
    tot_damage_per_event = DAMAGE_PROPERTY_USD + DAMAGE_CROPS_USD,
    county_fip = sprintf("%03d", CZ_FIPS),
    state_fip = sprintf("%02d", STATE_FIPS),
    county_fips = paste0(state_fip, county_fip),
    county_name = tolower(CZ_NAME)
  ) %>%
  group_by(county_fips) %>%
  summarise(total_damage = sum(tot_damage_per_event, na.rm = TRUE) / 100000) %>%
  filter(total_damage > 0)

# Join county cost data with unique county fips data
unique_county_fips <- urbnmapr::counties %>%
  distinct(county_fips, .keep_all = TRUE)

county_merged <- left_join(county_cost, urbnmapr::counties, by =c("county_fips"
) )%>%
  filter(!is.na(long))  # Remove rows with NA in 'long' column

# Update the CRS of the uscounties_sf object
uscounties_sf <- st_set_crs(uscounties_sf, value = NA)

# Now, mutate the county_name column
uscounties_sf <- uscounties_sf %>%
  mutate(county_name = tolower(county_name))
  
county_merged_poly <- left_join(county_merged, uscounties_sf, by = "county_fips")

# Plot the county map
ggplot() + 
  geom_sf(data = uscounties_sf) + 
  theme_map()

# Create plot for total damages by severe weather events
county_merged_df <- fortify(county_merged)

theme_set(theme_minimal() +
              theme(panel.grid.major = element_blank(),
                    plot.background = element_rect(fill = "#fdfdfd", colour = NA),
                    axis.title = element_blank(),
                    text = element_text(family = "Roboto Condensed"),
                    axis.text = element_blank(),
                    legend.position = "bottom"))


gg<- ggplot(county_merged_df, aes(long, lat, group = group, fill = total_damage)) +
  geom_polygon(color = "white", size = 0.055) + theme(legend.position="bottom", panel.border = element_blank())+
  labs(title = "Total Damages by Severe Weather 2017-2022",
       fill = "Total Damage (Million USD)") +
              scale_fill_viridis_c(name = "Total Damage (Million USD)",
                       trans = "log",
                       breaks = c(10, 100, 1000, 10000, 100000, 1000000),
                       labels = scales::comma) +theme_bw()+
  geom_polygon(data = urbnmapr::states, 
               aes(x = long, y = lat, group = group),
               fill = NA, color = "white", size = 1)
print(gg)

#zooming into Texas an dLouisiana
library(ggplot2)
library(dplyr)
library(patchwork)

# Assuming 'county_merged_df' contains data for multiple counties
library(cowplot)

# Filter data for Texas and Louisiana

zoom_counties <- county_merged_df %>%
  filter(state_name %in% c("Texas", "Louisiana"))

# Create the two additional maps for Texas and Louisiana
texas_map<- ggplot(zoom_counties %>% filter(state_name == "Texas"), aes(long, lat, group = group, fill = tot_damage))+
  geom_polygon(color = "white", size = 0.055) + theme(legend.position="bottom", panel.border = element_blank())+
  labs(title = "Total Damages by Severe Weather 2017-2022",
       fill = "Total Damage (Million USD)") +
              scale_fill_viridis_c(name = "Total Damage; Texas (Million USD)",
                       trans = "log",
                       breaks = c(10, 100, 1000, 10000, 100000, 1000000),
                       labels = scales::comma) +theme_bw()+
  geom_polygon(data = urbnmapr::states, 
               aes(x = long, y = lat, group = group),
               fill = NA, color = "white", size = 1)
print(texas_map)


louisiana_map<- ggplot(zoom_counties %>% filter(state_name == "Louisiana"), aes(long, lat, group = group, fill = tot_damage))+
  geom_polygon(color = "white", size = 0.055) + theme(legend.position="bottom", panel.border = element_blank())+
  labs(title = "Total Damages by Severe Weather 2017-2022",
       fill = "Total Damage (Million USD)") +
              scale_fill_viridis_c(name = "Total Damage ;Louisiana (Million USD)",
                       trans = "log",
                       breaks = c(10, 100, 1000, 10000, 100000, 1000000),
                       labels = scales::comma) +theme_bw()+
  geom_polygon(data = urbnmapr::states, 
               aes(x = long, y = lat, group = group),
               fill = NA, color = "white", size = 1)
print(louisiana_map)



# Print the combined plots
#print(combined_plots)
#plot the changes over time
#library(gganimate)

#g <- gg + transition_time(year) +
 # labs(title = 'Date: {year}')

#animate(p, end_pause=30)


```

##this visual isn't super informative, so let's instead plot changes in damage within a 5-year period.
# First, we Filter data for the desired 5-year period

```{r}
# Group data by county and calculate total damage for each county
if (!all(c("DAMAGE_PROPERTY_USD", "DAMAGE_CROPS_USD", "CZ_FIPS", "STATE_FIPS", "CZ_NAME", "YEAR") %in% names(storms))) {
  stop("Required columns are missing in the 'storms' data frame.")
}

# Perform data manipulation
county_cost <- storms %>%
  mutate(
    tot_damage_per_event = DAMAGE_PROPERTY_USD + DAMAGE_CROPS_USD,
    county_fip = sprintf("%03d", CZ_FIPS),  # Use sprintf to add leading zeros
    state_fip = sprintf("%02d", STATE_FIPS),  # Use sprintf to add leading zeros
    county_fips = paste0(state_fip, county_fip),
    county_name = tolower(CZ_NAME)
  )

# Filter and summarize data for 2017
storms_filtered_2017 <- county_cost %>%
  filter(YEAR == 2017) %>%
  group_by(county_fips) %>%
  summarise(damage_2017 = sum(tot_damage_per_event, na.rm = TRUE))

# Filter and summarize data for 2022
storms_filtered_2022 <- county_cost %>%
  filter(YEAR == 2022) %>%
  group_by(county_fips) %>%
  summarise(damage_2022 = sum(tot_damage_per_event, na.rm = TRUE))

# Join the datasets to calculate the difference in total damage
county_damage_diff <- left_join(storms_filtered_2022, storms_filtered_2017, by = "county_fips")

# Calculate damage difference
county_damage_diff <- county_damage_diff %>%
  mutate(damage_difference = damage_2022 - damage_2017)  # Correct calculation

# Obtain unique county FIPS codes
unique_county_fips <- urbnmapr::counties %>%
  distinct(county_fips, .keep_all = TRUE)

# Merge datasets
year_diff_merged <- left_join(county_damage_diff, unique_county_fips, by = "county_fips") %>%
  filter(!is.na(lat))

year_diff_df <- fortify(year_diff_merged)

library(ggplot2)

# Set theme
theme_set(theme_minimal() +
              theme(panel.grid.major = element_line(size = 0),
                    plot.background = element_rect(fill = "#fdfdfd", colour = NA),
                    axis.title = element_blank(),
                    text = element_text(family = "Roboto Condensed"),
                    axis.text = element_blank(),
                    legend.position = "bottom"))

# Use diverging color scale for positive and negative values
gg_diff <- ggplot(year_diff_df, aes(long, lat, group = group, fill = damage_difference)) +
  geom_polygon(color = "white", size = 0.125) +
  labs(title = "Total Damages by Severe Weather 2017-2022",
       fill = "Total Damage (Million USD)") +
  scale_fill_viridis_c(name = "Total Damage (Million USD)",
                       option = "magma",  # Choose a color palette suitable for diverging data
                       breaks = c(-1000000, -10000, -1000, -100, 0, 100, 1000, 10000, 100000, 1000000),
                       labels = scales::comma) +
  theme_minimal() +  # Applying minimal theme
  theme(legend.position = "bottom",  # Adjust legend position
        panel.border = element_blank()) +  # Remove panel border
  geom_polygon(data = urbnmapr::states, 
               aes(x = long, y = lat, group = group),
               fill = NA, color = "white", size = 1)

# Print the plot
print(gg_diff)


```

```

##Q1C, Provide an alternative map, in which you highlight the density of severe events by focusing on the variables of injuries and/or deaths associated with storms.

Discuss briefly which of the two approaches provides a better visual summary of the distribution of the destructive effects of storms.

My choice of dot density map:
- color code by threshold of density and intensity/ number of deaths/ scale of damage
- dimensions of interest: deaths p/1000 inhabitants
- deaths_direct vs deaths_indirect
-ratio of injuries direct/indirect and ratio of deaths
- proportion of deaths that were indirect/ direct out of total deaths
- proportional change of deaths and injuries by county
- add prism map for population density
- create facets by season 

##OBSERVATIONS:
Looking at the output, I prefer the insights that we are able to derive from the bubble map, opposed to the choropleth maps . Clearly, event patterns are not equally distributed within regions or event states, and their clustering of densities d onot follow these geographic boundaries. As such, the bubblemap provides a more truthful and accurate portrayal of severe weather patterns, and provides additional dimensionality through the geometric feature of the bubble diameter.  

```{r}
#First, lets do some data preprocessing. We'll start by developing metric for the severity of events, according to the proportion of combined injuries/deaths that were deaths. Consequently, the bubbles will be sized according to the total number of weather events in the time frame.

#later , we complete our preprocessing by eliminating any rows with NA values 
#completing some recoding to segment our disasters by season

#get map and polygon of US
# Get the world polygon and extract UK
library(dplyr)
library(maps)
library(viridis)
library(urbnmapr)
 

storms_fat <- storms %>%
  mutate(
    county_fip = sprintf("%03d", CZ_FIPS),
    state_fip = sprintf("%02d", STATE_FIPS),
    county_fips = paste0(state_fip, county_fip)
  )

#Now, we can add our dot density map visualizations

storms_fat2 <- storms_fat %>%
  filter(!is.na(DEATHS_DIRECT) & !is.na(INJURIES_DIRECT) & BEGIN_LAT != "NA" & BEGIN_LON != "NA") %>%
  filter(DEATHS_DIRECT>0)%>%
  mutate(fatality_rate = DEATHS_DIRECT / (DEATHS_DIRECT + INJURIES_DIRECT),
         season = case_when(
           MONTH_NAME %in% c("January", "February", "December") ~ "Winter",
           MONTH_NAME %in% c("March", "April", "May") ~ "Spring",
           MONTH_NAME %in% c("June", "July", "August") ~ "Summer",
           MONTH_NAME %in% c("September", "October", "November") ~ "Fall"
         ))

#download county-level shp files 
#county_shapefile <- urbnmapr::counties() %>%
  #mutate(county_name = tolower(county_name)) %>%
  #mutate(county_fips = paste0(STATEFP, COUNTYFP)) %>%
 # distinct(county_fips, .keep_all = TRUE)
#merge shape files and storm event data
#fatality_merged <- left_join(county_shapefile, storms_fat2, "county_fips")

#now that we've merged our shapefiles and data, we can begin to implement our dot density map, first by laying out individual points 


# Download county-level shapefiles 
county_shapefile <- counties() %>%
  mutate(county_name = tolower(NAME),
         county_fips = paste0(STATEFP, COUNTYFP)) %>%
  distinct(county_fips, .keep_all = TRUE)

# Merge shapefiles and storm event data
fatality_merged <- left_join(county_shapefile, storms_fat2, by = "county_fips") %>%
  arrange(DEATHS_DIRECT)

# Get US county map data
us.counties <- map_data("county")

# Plot
library(viridis)
ggplot() +
  geom_polygon(data = us.counties, aes(x = long, y = lat, group = group), fill = "grey", alpha = 0.3) +
  geom_point(data = fatality_merged, aes(x = BEGIN_LON, y = BEGIN_LAT, size = DEATHS_DIRECT, color = season)) +
  scale_size_continuous(range = c(0, 1)) +
  scale_color_viridis(discrete = TRUE, name = "Season") +  
  labs(x = "Longitude", y = "Latitude", title = "Fatality Rate by Season", size = "Deaths") +  
  theme_void() +
  theme(legend.position = "right") +
  coord_map()

#creating a map for death rate by plotting fraction of direct deaths out of deaths+injuries

fatality_merged <- fatality_merged %>%
  mutate(fatality_fraction = DEATHS_DIRECT / (DEATHS_DIRECT + INJURIES_DIRECT))

# Create breaks for the color scale
mybreaks <- c(0,10, 100, 1000, 10000)

# Now plot the map
season_colors <- c("Spring" = "purple", "Summer" = "blue", "Fall" = "grey", "Winter" = "grey")

# Plot the map
ggplot() +
  geom_polygon(data = us.counties, aes(x = long, y = lat, group = group), fill = "grey", alpha = 0.3) +
  geom_point(data = fatality_merged, aes(x = BEGIN_LON, y = BEGIN_LAT, size = fatality_fraction, color = season), alpha = 0.5) +
  scale_size_continuous(name = "fraction of direct deaths, out of total casualties", trans = "log", range = c(0, 1), breaks = mybreaks) +
  scale_alpha_continuous(name = "Total Deaths", trans = "log", range = c(0.1, 0.3), breaks = mybreaks) +
  scale_size_continuous(range = c(0, 3)) +
  scale_color_manual(name = "Season", values = season_colors) +  # Use custom color scale
  labs(x = "Longitude", y = "Latitude", title = "Fatality Rate per severe event, by Season", size = "Fraction of Deaths") +
  theme_void() +
  theme(
    legend.position = c(0.1, 0.5),
    legend.text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#f5f5f2", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    plot.title = element_text(size = 16, hjust = 0.1, color = "#4e4d47", margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm"))
  ) +
  coord_map()


library(RColorBrewer)


```

## NATIONAL BUBBLE MAP,BY SEVERE WEATHER EVENTS

Looking at our output, we clearly see that the summer and spring months give rise to  propensities of both higher frequencies of disaster events, but also more extreme weather events, shown by higher concentrations of fatality rates (number of deaths/(deaths+injuries))  

## SECONDARY BUBBLE MAP: Seeing how fatality rates compare to overall disaster events, including those which are minor and do not result in casualties.


```{r}
storms_fat <- storms %>%
  mutate(
    county_fip = sprintf("%03d", CZ_FIPS),
    state_fip = sprintf("%02d", STATE_FIPS),
    county_fips = paste0(state_fip, county_fip)
  )

storms_fat2 <- storms_fat %>%
  filter(!is.na(DEATHS_DIRECT) & !is.na(INJURIES_DIRECT) & BEGIN_LAT != "NA" & BEGIN_LON != "NA") %>%
 
  mutate(fatality_rate = DEATHS_DIRECT / (DEATHS_DIRECT + INJURIES_DIRECT),
         season = case_when(
           MONTH_NAME %in% c("January", "February", "December") ~ "Winter",
           MONTH_NAME %in% c("March", "April", "May") ~ "Spring",
           MONTH_NAME %in% c("June", "July", "August") ~ "Summer",
           MONTH_NAME %in% c("September", "October", "November") ~ "Fall"
         ))

# Download county-level shapefiles 

#county_shapefile <- counties() %>%
 # mutate(county_name = tolower(NAME),
  #       county_fips = paste0(STATEFP, COUNTYFP)) %>%
  #distinct(county_fips, .keep_all = TRUE)

# Merge shapefiles and storm event data
fatality_merged <- left_join(county_shapefile, storms_fat2, by = "county_fips") %>%
  arrange(DEATHS_DIRECT)

library(ggplot2)
library(sf)

# Set theme
theme_set(theme_minimal() +
              theme(panel.grid.major = element_line(size = 0),
                    plot.background = element_rect(fill = "#fdfdfd", colour = NA),
                    axis.title = element_blank(),
                    text = element_text(family = "Roboto Condensed"),
                    axis.text = element_blank(),
                    legend.position = "bottom"))

# Create the plot
# Plot the map
ggplot() +
  geom_polygon(data = us.counties, aes(x = long, y = lat, group = group), fill = "grey", alpha = 0.3) +
  geom_point(data = fatality_merged, aes(x = BEGIN_LON, y = BEGIN_LAT, color = season), alpha = 0.5) +
  scale_size_continuous(name = "fraction of direct deaths, out of total casualties", trans = "log", range = c(0, 1), breaks = mybreaks) +
  scale_alpha_continuous(name = "Total Deaths", trans = "log", range = c(0.1, 0.3), breaks = mybreaks) +
  scale_size_continuous(range = c(0, 3)) +
  scale_color_manual(name = "Season", values = season_colors) +  # Use custom color scale
  labs(x = "Longitude", y = "Latitude", title = "Fatality Rate per severe event, by Season", size = "Fraction of Deaths") +
  theme_void() +
  theme(
    legend.position = c(0.1, 0.5),
    legend.text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#f5f5f2", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    plot.title = element_text(size = 16, hjust = 0.1, color = "#4e4d47", margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm"))
  ) +
  coord_map()


```




REATE FACETS BY SEASON# Plot with facets by YEAR

```


```{r}

```

  ### Q2: Interactive map on Leaflet

    ##Q2A.)Create a leaflet map of the United States showing the location of severe weather events which result in at least one death (hint: use EVENT_TYPE). Ignore locations that fall outside the United States. Provide at least three pieces of information on the incident in a popup.


##LAYOUT FOR VISUALIZATION

We have already discovered some interesting trends in disaster event distribution by seasonality. To continue with the flow of our past data exploration, this leaflt visualization will serve the purpose of giving insight onto how the nature of severe weather events in the United States, at the local/regional level, might be geographically determined or influenced.

As such, I have imported a csv. file with the specific coastal classifications of each state, and will include this as a feature in the leaflet visualization.

```{r}

#installing appropriate packages
library(sf)             # for working with spatial data
library(dplyr)          # data frame manipulation
library(leaflet)        # because leaflet :)
library(htmltools)      # tools to support html workflow
library(rnaturalearth)  # interface to https://www.naturalearthdata.com/
library(leaflet.extras) # extending the leaflet.js
library(dplyr)
library(leaflet)

# Filter severe weather events with at least one death and within the United States
# Create a color palette with handmade bins.
mybins <- seq(0, 1, by=0.05)
mypalette <- colorBin( palette="YlOrBr", domain=quakes$mag, na.color="transparent", bins=mybins)

#download data fo0r coastline
list<-read.csv("/Users/inesperezalvarez-pallete/Desktop/coastal-states.csv")
list<-toupper(list)
# Reformat and remove forward slashes

coasts <- gsub("\"", "", list)    # Remove quotes
coasts_df <- data.frame(Coast = coasts)
library(dplyr)

# Function to extract states and coast types
extract_states_and_coasts <- function(list) {
  # Remove leading "C(" and trailing ")"
  list <- gsub("^C\\(|\\)$", "", list)
  # Split into separate elements
  elements <- unlist(strsplit(list, ", "))
  # Separate into states and coast types
  states <- elements[seq(1, 50)]
  coast_types <- elements[seq(51, 100)]
  # Create data frame
  df <- data.frame(states = states, coast_types = coast_types, stringsAsFactors = FALSE)
  return(df)
}


result_df <- extract_states_and_coasts(coasts)
#result_df$states[1] <- "ALABAMA"

#result_df$coast_types[1] <- "GULF COAST"

# Check column names and types in both data frames
str(result_df)
str(storms)


result_df$states <- as.character(result_df$states)
storms$STATE <- as.character(storms$STATE)

# Perform left join
coasts_merged <- left_join(result_df, storms, by = c("states" = "STATE"))

library(dplyr)
library(leaflet)

# Define boundaries for the continental United States
us_bounds <- list(
  lng1 = -125,  # Western boundary
  lng2 = -66,   # Eastern boundary
  lat1 = 24,    # Southern boundary
  lat2 = 49     # Northern boundary
)

# Filter out locations outside the United States
coasts_filtered <- coasts_merged %>%
  filter(
    EVENT_TYPE %in% c("Tornado", "Thunderstorm Wind", "Hail") & 
    DEATHS_DIRECT > 0 & 
    CZ_TYPE == "C" &
    BETWEEN(BEGIN_LAT, us_bounds$lat1, us_bounds$lat2) &  # Filter by latitude
    BETWEEN(BEGIN_LON, us_bounds$lng1, us_bounds$lng2)    # Filter by longitude
) %>%
select(BEGIN_LAT, BEGIN_LON, EVENT_TYPE, DEATHS_DIRECT, INJURIES_DIRECT, coast_types, DEATHS_INDIRECT)

# Define event colors
event_colors <- c(
  "Tornado" = "red",
  "Thunderstorm Wind" = "blue",
  "Hail" = "green"
)

# Create leaflet map
leaflet() %>%
  addTiles() %>%
  setView(lng = -95.7129, lat = 37.0902, zoom = 4) %>%  # Center the map on the US
  addCircleMarkers(
    data = coasts_filtered, 
    lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
    radius = ~DEATHS_DIRECT,  # Adjust the radius based on the number of deaths
    color = "red",  # Color code by event type
    fillColor = ~event_colors[EVENT_TYPE],  # Use custom color palette
    fillOpacity = 0.7,  # Adjust fill opacity
    popup = ~paste(
      "Event Type: ", EVENT_TYPE, "<br>",
      "Deaths: ", DEATHS_DIRECT, "<br>",
      "Injuries: ", INJURIES_DIRECT
    )
  ) %>%
  addLegend(position = "bottomright", 
            colors = unique(event_colors),  # Use unique event type colors for legend
            labels = names(event_colors),  # Label legend with event types
            title = "Event Type") %>%
  addLayersControl(
    overlayGroups = c("coast_types"),  # Add coast_types as an overlay group
    options = layersControlOptions(collapsed = FALSE)
  )
```

##Q2B.) 

  For this question, we can now integrate clusters according to the state/regional specifications, and see how the distribution of these events are determined by the coastal calssifications of the states. 
```{r}
library(leaflet)
library(leaflet.extras)

# Prepare a palette - manual colors according to EVENT_TYPE column
palPwr <- leaflet::colorFactor(
  palette = c(
    "Thunderstorm Wind" = "red", 
    "Tornado" = "goldenrod", 
    "Hail" = "steelblue"
  ), 
  domain = coasts_filtered$EVENT_TYPE
)

# Filter data by locations within the United States
us_coasts_filtered <- coasts_filtered %>%
  filter(BEGIN_LAT >= 24.396308 & BEGIN_LAT <= 49.384358 & 
           BEGIN_LON >= -125.0 & BEGIN_LON <= -66.93457)

# Prepare data frames for different types of coasts
gulf <- us_coasts_filtered %>% 
  filter(coast_types == "GULF COAST")
pacific <- us_coasts_filtered %>% 
  filter(coast_types == "PACIFIC OCEAN")
atlantic <- us_coasts_filtered %>% 
  filter(coast_types == "ATLANTIC OCEAN")
great_lakes <- us_coasts_filtered %>% 
  filter(coast_types == "GREAT LAKES COAST")

# Prepare leaflet plot
lplot <- leaflet(data = us_coasts_filtered) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addCircleMarkers(data = gulf, 
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = ~palPwr(EVENT_TYPE), # using color palette
                   clusterOptions = markerClusterOptions(),
                   group = "Gulf") %>%
  addCircleMarkers(data = pacific, 
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = ~palPwr(EVENT_TYPE), # using color palette
                   clusterOptions = markerClusterOptions(),
                   group = "Pacific") %>%
  addCircleMarkers(data = atlantic, 
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = ~palPwr(EVENT_TYPE), # using color palette
                   clusterOptions = markerClusterOptions(),
                   group = "Atlantic") %>%
  addCircleMarkers(data = great_lakes, 
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = ~palPwr(EVENT_TYPE), # using color palette
                   clusterOptions = markerClusterOptions(),
                   group = "Great Lakes") %>%
  addLegend(position = "bottomright",
            values = ~EVENT_TYPE,
            opacity = 0.7,
            pal = palPwr, # palette declared previously
            title = "EVENT TYPE") %>% 
  leaflet::addLayersControl(overlayGroups = c("Gulf", "Pacific", "Atlantic", "Great Lakes"),
                            options = layersControlOptions(collapsed = FALSE)) %>% 
  addResetMapButton()

lplot
```


##Q2C.) Finally, We apply clustering to our leaflet map.We immediately observe how our events have a tendency to aggregate along the Atlantic and Pacific Coastlines, specifically.


```{r}
`
```{r}
# prepare a palette - manual colors according to branch column
palPwr <- leaflet::colorFactor(palette = c("Thunderstorm Wind" = "red", 
                                           "Tornardo" = "goldenrod", 
                                           "Hail" = "steelblue"), 
                               domain = coasts_filtered$EVENT_TYPE)

in_coast <- coasts_filtered %>% 
  dplyr::filter(coast_types != "NONE") # a shortcut - all except judiciary are in Prague

no_coast <- coasts_filtered %>% 
  dplyr::filter(coast_types == "NONE" | coast_types=="\nNone") # a shortcut - all except 


# data frame of Brno points
gulf <- coasts_filtered %>% 
  filter(coast_types == "GULF COAST")

pacific <- coasts_filtered %>% 
  filter(coast_types == "PACIFIC OCEAN")

atlantic <- coasts_filtered %>% 
  filter(coast_types == "ATLANTIC OCEAN")

great_lakes <- coasts_filtered %>% 
  filter(coast_types == "GREAT LAKES COAST")

# first prepare a leaflet plot ...
library(leaflet.extras)

lplot <- leaflet(data = coasts_filtered) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addCircleMarkers(data = in_coast, # first group
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = palPwr(in_coast$EVENT_TYPE), # using already created palette
                   clusterOptions = markerClusterOptions(),
                   group = "coastal") %>% 
  addCircleMarkers(data = gulf, # second group
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = palPwr(gulf$EVENT_TYPE), # using already created palette
                   clusterOptions = markerClusterOptions(),
                   group = "Gulf") %>% 
  addCircleMarkers(data = no_coast, # third group
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = palPwr(no_coast$EVENT_TYPE), # using already created palette
                   clusterOptions = markerClusterOptions(),
                   group = "No Coast") %>% 
    addCircleMarkers(data = no_coast, # third group
                   lng = ~BEGIN_LON, lat = ~BEGIN_LAT,
                   radius = 10,
                   fillOpacity = 0.7,
                   stroke = FALSE,
                   popup = ~paste(
                     "Event Type: ", EVENT_TYPE, "<br>",
                     "Deaths: ", DEATHS_DIRECT, "<br>",
                     "Injuries: ", INJURIES_DIRECT
                   ),
                   color = palPwr(no_coast$EVENT_TYPE), # using already created palette
                   clusterOptions = markerClusterOptions(),
                   group = "No Coast") %>%
  addLegend(position = "bottomright",
            values = ~EVENT_TYPE,
            opacity = 0.7,
            pal = palPwr, # palette declared previously
            title = "EVENT TYPE") %>% 
  leaflet::addLayersControl(overlayGroups = c("Coastal", "Gulf", "No Coast"),
                            options = layersControlOptions(collapsed = FALSE)) %>% 
  addResetMapButton()
lplot #
```
```
###BONUS QUESTION: ATTEMPT


```{r}
library(dplyr)
library(geosphere)

# Load the data of severe weather events and the Top 100 largest cities
# Assuming you have 'severe_weather_events' and 'top_100_cities' datasets available

# Step 1: Find the nearest city for each severe weather event
nearest_city <- lapply(seq_len(nrow(severe_weather_events)), function(i) {
  event <- severe_weather_events[i, ]
  distances <- apply(top_100_cities[, c("Longitude", "Latitude")], 1, function(x) distHaversine(x, event[, c("BEGIN_LON", "BEGIN_LAT")]))
  nearest_city_index <- which.min(distances)
  return(top_100_cities[nearest_city_index, ])
})

nearest_city_df <- do.call(rbind, nearest_city)


severe_weather_events$Distance_to_nearest_city <- distHaversine(
  cbind(severe_weather_events$BEGIN_LON, severe_weather_events$BEGIN_LAT),
  cbind(nearest_city_df$Longitude, nearest_city_df$Latitude)
)

scatter_plot <- ggplot(severe_weather_events, aes(x = Population, y = DEATHS_DIRECT)) +
  geom_point() +
  labs(x = "City Population", y = "Deaths Directly Caused by Weather Event") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()

scatter_plot_by_event <- ggplot(severe_weather_events, aes(x = Population, y = DEATHS_DIRECT, color = EVENT_TYPE)) +
  geom_point() +
  labs(x = "City Population", y = "Deaths Directly Caused by Weather Event", color = "Event Type") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()


print(scatter_plot)
print(scatter_plot_by_event)
```




